Determining the alternatives for scalar implicature

### 2016-02-02 Paper/Paper.Rmd
Final read

On each trial participants were presented with a target scalar item from five scales, selected from the entailment items used in @vantiel2014b. These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the the food was \____," with a target scalar presented in the blank. Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.

>>>>

On each trial participants were presented with a target scalar item from five scales, selected from the entailment items used in @vantiel2014b. These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the food was \____," with a target scalar presented in the blank. Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.

### 2016-02-02 Paper/Paper.tex
Final read

On each trial participants were presented with a target scalar item from
five scales, selected from the entailment items used in {van Tiel} et
al. (2014). These were embedded in a sentence such as, ``In a recent
restaurant review someone said they thought the the food was \_\_\_\_,"
with a target scalar presented in the blank. Participants were then
asked to generate plausible alternatives by responding to the question,
``If they'd felt differently about the food, what other words could they
have used instead of \_\_\_\_?" They were prompted to generate three
unique alternatives.

>>>>

On each trial participants were presented with a target scalar item from
five scales, selected from the entailment items used in {van Tiel} et
al. (2014). These were embedded in a sentence such as, ``In a recent
restaurant review someone said they thought the food was \_\_\_\_," with
a target scalar presented in the blank. Participants were then asked to
generate plausible alternatives by responding to the question, ``If
they'd felt differently about the food, what other words could they have
used instead of \_\_\_\_?" They were prompted to generate three unique
alternatives.
